Action alternatives & confidence factor

### 2023-05-05 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/action_alternatives_confidence_factor.Rmd
update R script action alternatives

library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl, 
      gridExtra,
      janitor,
      RColorBrewer,
      cowplot)

@@

# SJT CM
df_sjt <- read_csv2(file = "data/SJT.csv",
                    locale = locale(decimal_mark = ",")) %>% 
  select(UI06_05,
         SJT_KF_gek) %>%
  filter(UI06_05 %in% c(101:126, 201:228),
         !UI06_05 %in% c(204, 226)
         ) %>% 
  na.omit() %>% 
  rename("id" = "UI06_05",
         "sjt" = "SJT_KF_gek")

# ACTION ALTERNATIVES count
df_alternatives_count <- read_excel("data/coding_action_alternatives.xlsx") %>% 
  janitor::clean_names() %>% 
  group_by(id) %>% 
  # mutate(mean_code = mean(code)) %>% 
  distinct(count)

# ACTION ALTERNATIVES non-disruptive 
df_alternatives_nd <- read_excel("data/coding_action_alternatives.xlsx") %>% 
  janitor::clean_names() %>% 
  select(id, code) %>% 
  filter(code %in% c(1:3)) %>%
  group_by(id) %>%
  count() %>% 
  transmute(nd = n)

# merge data frames
# put all data frames into list
df_list <- list(df_sri,
                df_sjt,
                df_alternatives_count,
                df_alternatives_nd)

>>>>

library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl, 
      gridExtra,
      janitor,
      RColorBrewer,
      cowplot,
      zoo)

@@

# # SJT CM
# df_sjt <- read_csv2(file = "data/SJT.csv",
#                     locale = locale(decimal_mark = ",")) %>% 
#   select(UI06_05,
#          SJT_KF_gek) %>%
#   filter(UI06_05 %in% c(101:126, 201:228),
#          !UI06_05 %in% c(204, 226)
#          ) %>% 
#   na.omit() %>% 
#   rename("id" = "UI06_05",
#          "sjt" = "SJT_KF_gek")

# ACTION ALTERNATIVES count
df_alternatives_count <- read_excel("data/coding_action_alternatives.xlsx") %>% 
  na.locf() %>% 
  janitor::clean_names() %>% 
  group_by(id) %>% 
  # mutate(mean_code = mean(code)) %>% 
  mutate(count = max(count)) %>% 
  distinct(count)

# ACTION ALTERNATIVES non-disruptive 
df_alternatives_nd <- read_excel("data/coding_action_alternatives.xlsx") %>% 
  na.locf() %>% 
  janitor::clean_names() %>% 
  select(id, code) %>% 
  mutate(nd = 
           as.numeric(
             case_when(code > 3 ~ '0',
                       code <= 3 ~ '1',
                       TRUE ~ 'F'
                       )
             )
         ) %>%
  group_by(id) %>% 
  summarise(nd = sum(nd))

# merge data frames
# put all data frames into list
df_list <- list(df_sri,
                # df_sjt,
                df_alternatives_count,
                df_alternatives_nd)
